Compressive Channel Sensing of Multipath Millimeter Channel via a Beamspace Dantzig Selector and its Probabilitic Performance Bound

### 2019-02-01 ongoing/report/sec_3_theorems_and_proofs.tex
Finish Slides
Slightly fix notation

We first establish a technical lemma that shows \(\RM{supp}(g)\) has roughly cardinal \(L\), which guarantees, at the heart of the argument, that \(g\) is almost-sparse

@@

We apply DS to find \(\hat{g}\), setting
\Disp{
\gamma =\R{2 \log N_g}
}
Other values are of course possible, but this is enough to illustrate our purpose.
Also set for short
%
\Disp{
d =\hat{g} -g
}
%
And call
\begin{itemize}
\item \(\MC{A}\) be the largest \(s\) position of \(g\).
\item \(\MC{B}\) be the largest \(s\) position of \(d_{T(N_g) -\MC{A}}\).
\item \(\MC{C} =T(N_g) -\MC{A}\), i.e., the complementary index set of \(\MC{A}\).
\end{itemize}

Recall the definition () in section 1.

\Result
{Definition}
{
Suppose \(\M{A} \in \MB{M}_{\MB{K}} (N_1, N_2)\).
Let \(\MC{T} \subset T (N_2)\).
Denote as \(\M{A}_{\MC{T}}\) the columns of \(\M{A}\) having indices in \(\MC{T}\).
}

\Result
{Definition}
{
The function \(S:\; \MB{V}_{\MB{K}}(N) \mapsto \MB{V}_{\MB{K}}(N)\), \(N \in \MB{N}\), sorts the vector \(x \in \MB{V}_{\MB{K}}(N))\), so that
\Disp{
|S (x)(n_1)| \geq &|S (x)(n_2)|, \\
n_1 >&n_2,
\quad n_1, n_2 \in T (N) \NT
}
}

Note that there are infinitely many sorting functions depending on how to break the tie, but we fix any \(S\) throughout this article.
For definiteness, we may compare the first component first, and the second, and so on.
If still there is a tie for a certain component (for complex numbers), we compare the real part first, then the imaginary part.

\Result
{Definition}
{
Let function \(f:\; T (N) \mapsto \MB{R}_+\), \(N \in \MB{N}\), be given.
For \(x \in \MB{V}_{\MB{K}}(N)\), we say \(x\) is confined in sorted magnitude according to \(f\), if
\Disp{
|S(x) (n)| <&f (n),
\quad n \in T (N).
}
}

\Result
{Definition}
{
For \(\V{x} \in \MB{V}_{\MB{K}}(N)\), we say \(\V{x}\) is almost-\(s\)-sparse with \(\ell_1\)-residue \(R\), where \(s \ll N\), if
\Disp{
\sum_{n=s+1}^N |S(\V{x}) (n)|
\leq R.
}
}

\Result
{Lemma (Tentative)}
{
Suppose \(0 \leq \f \leq 2\pi k /N_H\), \(k =0, \dotsc, N_H-1\).
Let \(\f\) be given, and array response \(\V{a} (\f)\) defined as in ().
Then \(\V{a} (\f)\) is almost-\(L\)-sparse with \(\ell_1\)-residue \(R(N_H, L)\) to be
%
\Disp{
R
\leq 2 N_H \log \F{2\pi N_H}{L}.
}
}

The lemma is the key to estimating sparsity of \(h\), which we now show.
Recall the identity for Dirichlet kernel
%
\Disp{
D (\f')
:=&\left| \sum_{n=0}^{N_H-1} \RM{e}^{i n \f'} \right| \NT \\
=&\F{|\sin (N_H \f'/2)|}{|\sin (\f' /2)|},
\quad 0 \leq \f' \leq \pi
}
%
And recall the Taylor expansion of sin for the first two terms with respect to zero
%
\Disp{
\sin x =x -\F{x^3}{6} + \MC{O}(x^5), \quad x \ll 1
}
%
Actually it can be shown that we have a inequality
%
\Disp{
\left| x -\F{x^3}{6} \right| \leq \sin x, \quad -\pi \leq x \leq \pi
}
%
Applying the above inequality to the denominator and bounding the nominator by 1, we have
%
\Disp{
\left| D (\f') \right|
= \F{48}{|\f'^2 -24| |\f'|}
\quad 0 \leq \f' \leq \pi,
}

Particularly, for arbitrary \(\f\), find \(k\) so that
\Disp{
\eta :=&\f -\F{2\pi k}{N_H}, \\
\left| \eta \right|
\leq &\F{2\pi}{N_H}.
}
%
Then observe
\Disp{
\M{K}^\H \V{a}(\f) (k)
=\F{1}{N_H} D \left( \f -\F{2 \pi k} {N_H} \right)
}
So we need only bound
\Disp{
R(\eta)
:=\F{1}{N_H} \sum_{n_H =s}^{N_H -1} D \left( \eta +\F{2 \pi n_H} {N_H} \right)
}
By the approximation of rectangle to integral,
\Disp{
R(\eta) -\F{2\pi} {N_H}
\leq \F{1}{N_H} N_H \int_{\f'=2\pi L/N_H}^{2\pi} |D(\f')| d \f'
}
Bound \(D\) by above technique, meanwhile we notice \(\f' <24\).
\Disp{
R(\f)
\leq &\F{1}{2\pi} \int_{\f'=2\pi L/N_H}^{2\pi} \F{48}{(24 -\f'^2) \f'} d \f'
+\F{2\pi} {N_H} \NT \\
=&\F{1}{\pi} \log \F{2\pi N_H}{L}
-\F{1}{N_H} \log \F{4\pi^2 -24} {L^2/N_H^2 -24}
+\F{2\pi} {N_H}
}
Notice the argument of log in the second term \(<1\), and we drop that.
Also drop \(2\pi /N_H\) since it is small.
Furthermore the \(2\pi\) factor in log can be dropped too.
\Disp{
R(\f)
\leq \F{1}{\pi} \log \F{N_H}{L}.
}

\Result
{Lemma (Tentative)}
{
Let \(\f\) and \(\th\) be uniformly, independently distributed in \([0,2\pi)\), and linear array response \(\V{a}\) defined as in ().
Let \(\V{g}\) be defined as above.
Then \(\V{g}\) is almost-\(L\)-sparse with \(\ell_1\)-residue \(R(N_H, L)\) to be
%
\Disp{
R
\leq \F{L}{\pi^2} \left( \log \F{N_H}{L} \right)^2
}
}

@@

\Result
{Lemma}
{
Let \(P\) be i.i.d.\ Radmacher, as defined in Lemma ().
Then \(P\) is RIP according to \(\d\) for at least probability
\Disp{
1 -2 \left( \F{12}{\d} \right)^s \exp \left[ - \left( \F{\epsilon^2}{4} -\F{\epsilon^3}{6} \right) \F{\d}{2} N_p \right]
}
}

@@

We are ready to bound \(\| d \|_2^2\).
Using Lemma () again, we have
\Disp{
\| \V{d} \|_2^2
\leq &\|\V{d}_{\MC{A}\MC{B}}\|_2^2 +\F{1}{L} \|\V{d}_{\MC{C}}\|_1^2 \NT \\
\leq & \left( \F{\d_{3L}^2} {L^2 (1-\d_{2L})^2} +\F{1}{L} \right) \|\V{d}_{\MC{C}}\|_1^2
+\F{8 \d_{3L}} {L (1-\d_{2L})^2} \R{N_g \log N_g} \|\V{d}_{\MC{C}}\|_1 \NT \\
&\quad +\F{16}{(1-\d_{2L})^2} N_g \log N_g
}
Finally, plug in the bound for \(\|\V{d}_{\MC{C}}\|_1\), the last unknown, and we make use of the almost-sparsity condition of \(\|\V{d}_{\MC{C}}\|_1\).
There are several dozens of terms if we expand all.
but for simplicity, we keep only the leading term under the approximation
\Disp{
1 \ll L \ll N_g
}
And expand to the first order expressions containing \(\d_{2L}\) or \(\d_{3L}\) in the denominator using
\Disp{
\d_{2L} <\d_{3L} \ll 1.
}
Then
\Disp{
\|\V{d}\|_2^2
\leq \F{4}{\pi^4} \d_{3L}^4 (1-2\d_{2L}) L^4 ( \log N_H )^4
}

>>>>

We first establish a technical lemma that shows \(\RM{supp}(\V{g})\) has roughly cardinal \(L\), which guarantees, at the heart of the argument, that \(\V{g}\) is almost-sparse

@@

We apply DS to find \(\hat{\V{g}}\), setting
\Disp{
\gamma =\R{2 \log N_g}
}
Other values are of course possible, but this is enough to illustrate our purpose.
Also set for short
%
\Disp{
\V{d} =\hat{\V{g}} -\V{g}
}
%
And call
\begin{itemize}
\item \(\MC{A}\) be the largest \(s\) position of \(g\).
\item \(\MC{B}\) be the largest \(s\) position of \(d_{T(N_g) -\MC{A}}\).
\item \(\MC{C} =T \RB{ N_g } -\MC{A}\), i.e., the complementary index set of \(\MC{A}\).
\end{itemize}

Suppose \(\M{A} \in \MB{M}_{\MB{K}} \RB{ N_1, N_2 }\).
For brevity, let \(\MC{T} \subset T \RB{ N_2 }\).
Denote as \(\M{A}_{\MC{T}}\) the columns of \(\M{A}\) having indices in \(\MC{T}\).
Let \(S:\; \MB{V}_{\MB{K}}(N) \mapsto \MB{V}_{\MB{K}}(N)\), \(N \in \MB{N}\), be the sorting function for \(x \in \MB{V}_{\MB{K}}(N))\), so that
\Disp{
|S \RB{x} \DB{n_1}| \geq &|S \RB{x} \DB{n_2}|, \\
n_1 >&n_2,
\quad n_1, n_2 \in T\RB{N} \NT
}
Note that there are infinitely many sorting functions depending on how to break the tie, but we fix any \(S\) throughout this article.
For definiteness, we may compare the first component first, and the second, and so on.
If still there is a tie for a certain component (for complex numbers), we compare the real part first, then the imaginary part.

\Result
{Definition}
{
Let function \(f:\; T\RB{N} \mapsto \MB{R}_+\), \(N \in \MB{N}\), be given.
For \(x \in \MB{V}_{\MB{K}}(N)\), we say \(x\) is confined in sorted magnitude according to \(f\), if
\Disp{
|S(x) \DB{ n } | <&f (n),
\quad n \in T\RB{N}.
}
}

\Result
{Definition}
{
For \(\V{x} \in \MB{V}_{\MB{K}}(N)\), we say \(\V{x}\) is almost-\(s\)-sparse with \(\ell_1\)-residue \(R\), if
\Disp{
\sum_{n=s+1}^N |S(\V{x}) (n)|
\leq R.
}
}

\Result
{Lemma (Tentative)}
{
Suppose \(0 \leq \f \leq 2\pi k /N_H\), \(k =0, \dotsc, N_H-1\).
Let \(\f\) be given, and array response \(\V{a} (\f)\) defined as in ().
Then \(\V{a} (\f)\) is almost-\(L\)-sparse with \(\ell_1\)-residue \(R(N_H, L)\) to be
%
\Disp{
R
\leq \F{1}{\pi} \log \F{N_H}{L}.
}
}

We show the lemma, which is the key to bounding the sparsity of \(h\).
Recall the identity for Dirichlet kernel
%
\Disp{
D (\f')
:=&\Nm{ \sum_{n=0}^{N_H-1} \RM{e}^{i n \f'} } \NT \\
=&\F{|\sin (N_H \f'/2)|}{|\sin (\f' /2)|}, \\
\quad 0 \leq& \f' \leq \pi \NT
}
%
And recall the Taylor expansion of sin for the first two terms with respect to zero
%
\Disp{
\sin x =x -\F{x^3}{6} + \MC{O}(x^5), \quad x \ll 1
}
%
Actually it can be shown that we have a inequality
%
\Disp{
\Nm{ x -\F{x^3}{6} } \leq \Nm{ \sin x }, \\
-\pi \leq &x \leq \pi \NT
}
%
Applying the above inequality to the denominator and bounding the nominator by 1, we have
%
\Disp{
\Nm{ D (\f') }
= \F{48}{|\f'^2 -24| |\f'|}
\quad 0 \leq \f' \leq \pi. \NT
}

Particularly, for arbitrary \(\f\), find \(k\) so that
\Disp{
\eta :=&\f -\F{2\pi k}{N_H}, \\
\Nm{ \eta }
\leq &\F{2\pi}{N_H}.
}
%
Then observe
\Disp{
\RB{ \M{K}^\H \V{a}(\f) } \DB{ k }
=\F{1}{N_H} D \RB{ \f -\F{2 \pi k} {N_H} }
}
So we need only bound
\Disp{
R(\eta)
:=\F{1}{N_H} \sum_{n_H =s}^{N_H -1} D \RB{ \eta +\F{2 \pi n_H} {N_H} }
}
By the approximation of rectangle to integral,
\Disp{
R(\eta) -\F{2\pi} {N_H}
\leq \F{1}{N_H} N_H \int_{\f'=2\pi L/N_H}^{2\pi} |D(\f')| d \f'
}
Bound \(D\) by above technique, meanwhile we notice \(\f' <24\).
\Disp{
R(\f)
\leq &\F{1}{2\pi} \int_{\f'=2\pi L/N_H}^{2\pi} \F{48}{(24 -\f'^2) \f'} d \f'
+\F{2\pi} {N_H} \NT \\
=&\F{1}{\pi} \log \F{2\pi N_H}{L}
-\F{1}{N_H} \log \F{4\pi^2 -24} {L^2/N_H^2 -24}
+\F{2\pi} {N_H}
}
Notice the argument of log in the second term \(<1\), and we drop that.
Also drop \(2\pi /N_H\) since it is small.
Furthermore the \(2\pi\) factor in log can be dropped too.
\Disp{
R(\f)
\leq \F{1}{\pi} \log \F{N_H}{L}.
}

\Result
{Lemma (Tentative)}
{
Let \(\f\) and \(\th\) be uniformly, independently distributed in \([0,2\pi)\), and linear array response \(\V{a}\) defined as in ().
Let \(\V{g}\) be defined as above.
Then \(\V{g}\) is almost-\(L\)-sparse with \(\ell_1\)-residue \(R(N_H, L)\) to be
%
\Disp{
R
\leq \F{L}{\pi^2} \RB{ \log \F{N_H}{L} }^2
}
}

@@

\Result
{Lemma}
{
Let \(P\) be i.i.d.\ Radmacher, as defined in Lemma ().
Then \(P\) is RIP according to \(\d\) for at least probability
\Disp{
1 -2 \RB{ \F{12}{\d} }^s \exp \left[ - \RB{ \F{\epsilon^2}{4} -\F{\epsilon^3}{6} } \F{\d}{2} N_p \right]
}
}

@@

We are ready to bound \(\| d \|_2^2\).
Using Lemma () again, we have
\Disp{
\| \V{d} \|_2^2
\leq &\|\V{d}_{\MC{A}\MC{B}}\|_2^2 +\F{1}{L} \|\V{d}_{\MC{C}}\|_1^2 \NT \\
\leq & \RB{ \F{\d_{3L}^2} {L^2 (1-\d_{2L})^2} +\F{1}{L} } \|\V{d}_{\MC{C}}\|_1^2
+\F{8 \d_{3L}} {L (1-\d_{2L})^2} \R{N_g \log N_g} \|\V{d}_{\MC{C}}\|_1 \NT \\
&\quad +\F{16}{(1-\d_{2L})^2} N_g \log N_g
}
Finally, plug in the bound for \(\|\V{d}_{\MC{C}}\|_1\), the last unknown, and we make use of the almost-sparsity condition of \(\|\V{d}_{\MC{C}}\|_1\).
There are several dozens of terms if we expand all.
but for simplicity, we keep only the leading term under the approximation
\Disp{
1 \ll L \ll N_g
}
And expand to the first order expressions containing \(\d_{2L}\) or \(\d_{3L}\) in the denominator using
\Disp{
\d_{2L} <\d_{3L} \ll 1.
}
Then
\Disp{
\|\V{d}\|_2^2
\leq \F{4}{\pi^4} \d_{3L}^4 (1-2\d_{2L}) L^4 ( \log N_H )^4
}
